A Study of Institutional Spending on Open Access Publication Fees in Germany

### 2016-06-10 data/cost_data_uk/README.Rmd
minor

sum(tt$`Fees paid in GBP`)

@@

### wellcome 2014 - 2014

@@

>>>>

@@

### wellcome 2014 - 2015

@@

### open apc

```{r}
my_apc <- jsonlite::stream_in(file("../cr-apc-all.json"), verbose = FALSE)

# data cleaning
library(dplyr)
## remove Bielefelds Zero value
my_apc <- dplyr::filter(my_apc, euro > 0)
# remove intech book chapters
my_apc <-  dplyr::filter(my_apc, !is.na(journal_full_title))

# remove Austrian FWF data
my_apc <- dplyr::filter(my_apc, !institution == "FWF - Austrian Science Fund")
# data from 2014 and 2015
my_apc <- dplyr::filter(my_apc, period == "2015" | period == "2014")

aggregate(my_apc$euro, by = list(my_apc$is_hybrid, my_apc$period), sum)
aggregate(my_apc$euro, by = list(my_apc$is_hybrid, my_apc$period), mean)
aggregate(my_apc$euro, by = list(my_apc$is_hybrid, my_apc$period), length)
```
